Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
no more asterisks for times
add nit changes

However, there is a price for narrowing the synthesis domain so
dramatically: Many real data formats are almost, but not quite,
bijections. More often two related data formats have some data in
common, but also contain some differences. For instance, two related
tables might share four of five columns, but each has a different
fifth column. Alternately, one ad hoc configuration file might include
some file-specific meta data, such as a date, a time or a reference
number, whereas the other does not. Indeed of the 48 benchmark problems
described in Section \ref{sec:evaluation}, all of the benchmarks
taken from Flash Fill~\cite{flashfill} and all of the benchmarks that
synchronize between two ad hoc file formats have this 
characteristic, 48 benchmarks in total. Consequently, tools that search
only for strict bijections will rarely be applicable in practice.

@@

Initially, we hypothesized that extending the synthesis algorithms
of Miltner \ETAL~\cite{optician} to operate over symmetric rather than
bijective lenses
would be relatively straightforward:  Simply replace the bijective
combinators with symmetric ones 
and search using similar heuristics.  However, 
this naive approach runs into two difficulties.

@@

The second difficulty with synthesizing symmetric lenses is more
fundamental: While the number of bijective lenses between two
related formats is often tiny, the number of simple symmetric lenses is much larger. In
practice, the difference in cardinality means that when a search algorithm
returns the first bijective lens it finds, that lens has a good chance of being
the desired lens. In contrast, and to our initial surprise, experiments showed
that if a naive search algorithm selects the first simple symmetric lens it
finds, it is typically \emph{not} the desired lens.  The flexibility
that such lenses provide in eliding information 
generates an explosion of possible transformations. To disambiguate
between the many possible lenses, we need new 
principles for identifying the ``likely'' ones, and we need new
algorithms guided by those principles to
search the space of program transformations.

@@

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let salary = number | "unk"
let emp_salary = name . " " . name . ": " salary
let emp_salaries = "" | emp_salary . ("\n" emp_salary)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingC}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let company = (name . ("Co." | "Inc." | "Ltd.")) | "UNK" in
let emp_ins = name . " " . name "," company in
let header = "Name,Company" in
let emp_insurance = header . ("\n" . emp_ins)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingD}{\box0}

@@

This infrastructure gives us what we need to find likely satisfying lenses from
a collection of satisfying lenses. All such lenses must synchronize data between
the same two SREs $\Regex$ and $\RegexAlt$. For any such lens $\Lens$, we can
calculate the expected number of bits required to recover a string $t$ in
$\LanguageOf{\RegexAlt}$ from a synchronized string $s$ in
$\LanguageOf{\Regex}$. This expectation is the \emph{conditional entropy of
  $\Regex$ given $\RegexAlt$ and $\Lens$}, formally $\sum_{s \in
  \Regex}\ProbabilityOf{\Regex}{s}*\EntropyOf{\SetOf{t \SuchThat
    \Lens.\PutROf{s}{t} = t}}$. The likelihood we assign to $\Lens$ is the sum
of the conditional entropy of $\Regex$ given $\RegexAlt$ and $\Lens$ and the
conditional entropy of $\RegexAlt$ given $\Regex$ and $\Lens$. This metric
assigns higher entropy (or cost) to lenses where knowing the string
on one side 
provides little information about the string on the other side. 
It assigns zero entropy to bijections because given a string $s \in \Regex$,
the bijection exactly determines
the corresponding string in 
$\RegexAlt$.

@@

    & =
    & $\Sigma_{\String = \String_1\String_2}\ProbabilityOf{\Regex_1}{\String_1}*\ProbabilityOf{\Regex_2}{\String_2}$ \\

    $\ProbabilityOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability}}{\String}$
    & =
    & $\Probability * \ProbabilityOf{\Regex_1}{\String} +
      (1-\Probability) * \ProbabilityOf{\Regex_2}{\String}$\\

    $\ProbabilityOf{\PRegexStar{\Regex}{\Probability}}{\String}$
    & =
    & $\Sigma_n \Sigma_{\String = \String_1 \ldots \String_n}\Probability^n*(1-\Probability)*\Pi_{i=1}^n\ProbabilityOf{\Regex}{\String_i}$\\
  \end{tabular}
\end{center}

\begin{figure}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)*\Probability_2}{1 - \Probability_1 * \Probability_2}})}{\Probability_1*\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
  \caption{Stochastic Regular Expression Star-Semiring Equivalence}
  \label{fig:ssr-sre}
\end{figure}

@@

    $\EntropyOf{\PRegexOr{\Regex}{\RegexAlt}{\Probability}}$
    & =
    & $\Probability*(\EntropyOf{\Regex} - \Log_2(\Probability)) + (1-\Probability)*(\EntropyOf{\RegexAlt} - \Log_2(1-\Probability))$\\
  \end{tabular}
\end{center}
We have proven that this syntactic computation corresponds to the entropy of the
stochastic regular expression.

@@

    $\REntropyOf{\PRegexStar{\RegexAlt}{\ProbabilityAlt} \Given \IterateLensOf{\Lens}, \PRegexStar{\Regex}{\Probability}}$
    & =
    & $\frac{\Probability}{1-\Probability}(\REntropyOf{\RegexAlt \Given \Lens, \Regex})$\\

@@

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1} ) + (1-\Probability)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\RegexAlt \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + (1-\Probability)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2})$\\

@@

As these DNF regular expressions are \emph{stochastic}, they are annotated with
probabilities to express a probability distribution, in addition to a
language. \saz{I find the use of asterisk for the $\times$ or $\cdot$ or maybe
  just juxtaposition slightly jarring.}
\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\PRegexStar{\DNFRegex}{\Probability}}{\String}$
    & =
    & $\Sigma_n \Sigma_{\String = \String_1 \ldots \String_n}\Probability^n*(1-\Probability)*\Pi_{i=1}^n\ProbabilityOf{\DNFRegex}{\String_i}$\\

@@

    $\ProbabilityOf{\DNFOf{(\Sequence_1,\Probability_1) \DNFSep \ldots \DNFSep (\Sequence_n,\Probability_n)}}{\String}$
    & =
    & $\Sigma_{i=1}^n\Probability_i * \ProbabilityOf{\Sequence_i}{\String}$\\
  \end{tabular}
\end{center}

@@

  $\ConcatDNF{} \OfType{} \ArrowTypeOf{\DNFRegexType{}}{\ArrowTypeOf{\DNFRegexType{}}{\DNFRegexType{}}}$\\
  $\ConcatDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}=$\\
      $\DNFLeft (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_1},\Probability_1*\ProbabilityAlt_1)\DNFSep \ldots
      \DNFSep
      (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_m},\Probability_1*\ProbabilityAlt_m)\DNFSep
      \ldots$\\
      $\DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_1},\Probability_n*\ProbabilityAlt_1)\DNFSep
      \ldots \DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_m},\Probability_n * \ProbabilityAlt_m) \DNFRight$

@@

  $\OrDNF{}_{\Probability} \OfType{}
  \ArrowTypeOf{\DNFRegexType{}}{\ArrowTypeOf{\DNFRegexType{}}{\DNFRegexType{}}
  }$ \\
  $\OrDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}{\Probability} =$\\
  $\DNFOf{(\Sequence_1,\Probability_1*\Probability)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n*\Probability)\DNFSep(\SequenceAlt_1,\ProbabilityAlt_1*(1-\Probability))\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m*(1-\Probability))}$

@@

\subsection{\GreedySynth}
\label{subsec:greedy-synth}
The synthesis procedure comprises three algorithms: one that greedily finds
symmetric DNF lenses (\GreedySynth), one that greedily finds symmetric sequence
lenses (\GreedySeqSynth), and one that finds symmetric atom lenses
(\AtomSynth{}). These three algorithms are hierarchically structured:
\GreedySynth relies on \GreedySeqSynth, \GreedySeqSynth relies on \AtomSynth,
and \AtomSynth rlies on \GreedySynth. The structure of the algorithms mirrors
the structure of symmetric DNF lenses and \SDNFREabbrevs. We describe this
synthesis algorithm using the running example of searching for a lens between
\lstinline{"" | name.name*} and \lstinline{"" | name}.

@@

In our example, \GreedySynth might first pop the sequence pair \lstinline{""} and
\lstinline{""}, because there is a bijective sequence lens between them. As neither
\lstinline{""} is involved in a sequence lens, this lens is considered useful.
Next, the sequence lens between \lstinline{name.name*} and
\lstinline{name} would be popped: while that lens is not bijective: it is still
better than the alternatives. As all sequences are now involved in sequence lenses,
and there are no examples to make other lenses useful, no further sequence
lenses would be added to the lens builder.

>>>>

However, there is a price for narrowing the synthesis domain so
dramatically: Many real data formats are almost, but not quite,
bijections. More often two related data formats have some data in
common, but also contain some differences. For instance, two related
tables might share four of five columns, but each has a different
fifth column. Alternately, one ad hoc configuration file might include
some file-specific meta data, such as a date, a time or a reference
number, whereas the other does not. Indeed of the 48 benchmark problems
described in Section \ref{sec:evaluation}, all of the benchmarks
taken from Flash Fill~\cite{flashfill} and many of the benchmarks that
synchronize between two ad hoc file formats have this 
characteristic, 13 benchmarks in total. Consequently, tools that search
only for strict bijections are often not applicable in practice.

@@

Initially, we hypothesized that extending the synthesis algorithms
of Miltner \ETAL~\cite{optician} to operate over symmetric rather than
bijective lenses
would be relatively straightforward:  Simply replace the bijective
combinators with symmetric ones 
and search using similar heuristics.  However, 
this na\"ive approach runs into two difficulties.

@@

The second difficulty with synthesizing symmetric lenses is more
fundamental: While the number of bijective lenses between two
related formats is often tiny, the number of simple symmetric lenses is much larger. In
practice, the difference in cardinality means that when a search algorithm
returns the first bijective lens it finds, that lens has a good chance of being
the desired lens. In contrast, and to our initial surprise, experiments showed
that if a na\"ive search algorithm selects the first simple symmetric lens it
finds, it is typically \emph{not} the desired lens.  The flexibility
that such lenses provide in eliding information 
generates an explosion of possible transformations. To disambiguate
between the many possible lenses, we need new 
principles for identifying the ``likely'' ones, and we need new
algorithms guided by those principles to
search the space of program transformations.

@@

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let salary = number | "unk"
let emp_salary = name . " " . name . ": " salary
let emp_salaries = "" | emp_salary . ("\n" emp_salary)$^*$
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingC}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let company = (name . ("Co." | "Inc." | "Ltd.")) | "UNK" in
let emp_ins = name . " " . name "," company in
let header = "Name,Company" in
let emp_insurance = header . ("\n" . emp_ins)$^*$
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingD}{\box0}

@@

This infrastructure gives us what we need to find likely satisfying lenses from
a collection of satisfying lenses. All such lenses must synchronize data between
the same two SREs $\Regex$ and $\RegexAlt$. For any such lens $\Lens$, we can
calculate the expected number of bits required to recover a string $t$ in
$\LanguageOf{\RegexAlt}$ from a synchronized string $s$ in
$\LanguageOf{\Regex}$. This expectation is the \emph{conditional entropy of
  $\Regex$ given $\RegexAlt$ and $\Lens$}, formally $\sum_{s \in
  \Regex}\ProbabilityOf{\Regex}{s}\EntropyOf{\SetOf{t \SuchThat
    \Lens.\PutROf{s}{t} = t}}$. The likelihood we assign to $\Lens$ is the sum
of the conditional entropy of $\Regex$ given $\RegexAlt$ and $\Lens$ and the
conditional entropy of $\RegexAlt$ given $\Regex$ and $\Lens$. This metric
assigns higher entropy (or cost) to lenses where knowing the string
on one side 
provides little information about the string on the other side. 
It assigns zero entropy to bijections because given a string $s \in \Regex$,
the bijection exactly determines
the corresponding string in 
$\RegexAlt$.

@@

    & =
    & $\Sigma_{\String = \String_1\String_2}\ProbabilityOf{\Regex_1}{\String_1}\ProbabilityOf{\Regex_2}{\String_2}$ \\

    $\ProbabilityOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability}}{\String}$
    & =
    & $\Probability\ProbabilityOf{\Regex_1}{\String} +
      (1-\Probability)\ProbabilityOf{\Regex_2}{\String}$\\

    $\ProbabilityOf{\PRegexStar{\Regex}{\Probability}}{\String}$
    & =
    & $\Sigma_n \Sigma_{\String = \String_1 \ldots \String_n}\Probability^n(1-\Probability)\Pi_{i=1}^n\ProbabilityOf{\Regex}{\String_i}$\\
  \end{tabular}
\end{center}

\begin{figure}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)\Probability_2}{1 - \Probability_1\Probability_2}})}{\Probability_1\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
  \caption{Stochastic Regular Expression Star-Semiring Equivalence}
  \label{fig:ssr-sre}
\end{figure}

@@

    $\EntropyOf{\PRegexOr{\Regex}{\RegexAlt}{\Probability}}$
    & =
    & $\Probability(\EntropyOf{\Regex} - \Log_2(\Probability)) + (1-\Probability)(\EntropyOf{\RegexAlt} - \Log_2(1-\Probability))$\\
  \end{tabular}
\end{center}
We have proven that this syntactic computation corresponds to the entropy of the
stochastic regular expression.

@@

    $\REntropyOf{\PRegexStar{\RegexAlt}{\ProbabilityAlt} \Given \IterateLensOf{\Lens}, \PRegexStar{\Regex}{\Probability}}$
    & =
    & $\frac{\Probability}{1-\Probability}\REntropyOf{\RegexAlt \Given \Lens, \Regex}$\\

@@

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1} + (1-\Probability)\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\REntropyOf{\RegexAlt \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1} + (1-\Probability)\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2}$\\

@@

As these DNF regular expressions are \emph{stochastic}, they are annotated with
probabilities to express a probability distribution, in addition to a
language.
\begin{center}
  \begin{tabular}{rcl}
    $\ProbabilityOf{\PRegexStar{\DNFRegex}{\Probability}}{\String}$
    & =
    & $\Sigma_n \Sigma_{\String = \String_1 \ldots \String_n}\Probability^n(1-\Probability)\Pi_{i=1}^n\ProbabilityOf{\DNFRegex}{\String_i}$\\

@@

    $\ProbabilityOf{\DNFOf{(\Sequence_1,\Probability_1) \DNFSep \ldots \DNFSep (\Sequence_n,\Probability_n)}}{\String}$
    & =
    & $\Sigma_{i=1}^n\Probability_i\ProbabilityOf{\Sequence_i}{\String}$\\
  \end{tabular}
\end{center}

@@

  $\ConcatDNF{} \OfType{} \ArrowTypeOf{\DNFRegexType{}}{\ArrowTypeOf{\DNFRegexType{}}{\DNFRegexType{}}}$\\
  $\ConcatDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}=$\\
      $\DNFLeft (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_1},\Probability_1\ProbabilityAlt_1)\DNFSep \ldots
      \DNFSep
      (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_m},\Probability_1\ProbabilityAlt_m)\DNFSep
      \ldots$\\
      $\DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_1},\Probability_n\ProbabilityAlt_1)\DNFSep
      \ldots \DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_m},\Probability_n\ProbabilityAlt_m) \DNFRight$

@@

  $\OrDNF{}_{\Probability} \OfType{}
  \ArrowTypeOf{\DNFRegexType{}}{\ArrowTypeOf{\DNFRegexType{}}{\DNFRegexType{}}
  }$ \\
  $\OrDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}{\Probability} =$\\
  $\DNFOf{(\Sequence_1,\Probability_1\Probability)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n\Probability)\DNFSep(\SequenceAlt_1,\ProbabilityAlt_1(1-\Probability))\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m(1-\Probability))}$

@@

\subsection{\GreedySynth}
\label{subsec:greedy-synth}
The synthesis procedure comprises three algorithms: one that greedily finds
symmetric DNF lenses (\GreedySynth), one that greedily finds symmetric sequence
lenses (\GreedySeqSynth), and one that finds symmetric atom lenses
(\AtomSynth{}). These three algorithms are hierarchically structured:
\GreedySynth relies on \GreedySeqSynth, \GreedySeqSynth relies on \AtomSynth,
and \AtomSynth rlies on \GreedySynth. The structure of the algorithms mirrors
the structure of symmetric DNF lenses and \SDNFREabbrevs. We describe this
synthesis algorithm using the running example of searching for a lens between
\lstinline{"" | name.name$^*$} and \lstinline{"" | name}.

@@

In our example, \GreedySynth might first pop the sequence pair \lstinline{""} and
\lstinline{""}, because there is a bijective sequence lens between them. As neither
\lstinline{""} is involved in a sequence lens, this lens is considered useful.
Next, the sequence lens between \lstinline{name.name$^*$} and
\lstinline{name} would be popped: while that lens is not bijective: it is still
better than the alternatives. As all sequences are now involved in sequence lenses,
and there are no examples to make other lenses useful, no further sequence
lenses would be added to the lens builder.
